---
title: "Weight of Fish"
author: "Isai Bercian"
date: "April 13 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fishdata=read.csv(file="Fish.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Perchdata=filter(Fishdata, Species=="Perch" )
 Perchdata = subset (Perchdata, select = -Species)
```


## Inferential Results


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The best model uses two variables: H-W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perchdata)
fullup <- lm(Weight~.,data=Perchdata)
summary(best.model)
```

The p-value here is so small that it shows how this model is an excellent fit.

```{r}
anova(fullup,best.model)
```
The p-value is 0.879 which means that there is really no difference between using the model that has all of the data vs. The model that uses only 2 variables.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



# Bream

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Breamdata=filter(Fishdata, Species=="Bream" )
 Breamdata = subset (Breamdata, select = -Species)
```



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The best model is the one that uses three variables: L1-H-W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```
```{r}
best.model <- lm(Weight~Length2+Height,data=Breamdata)
fullup <- lm(Weight~.,data=Breamdata)
summary(best.model)
```
```{r}
anova(fullup,best.model)
```

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

The p-value is to large to say that there is a difference between utilizing the best model which utilizes three variables and the best model that utilizes two.

# Smelt

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Smeltdata=filter(Fishdata, Species=="Smelt" )
 Smeltdata = subset (Smeltdata, select = -Species)
```



## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
## Which is best??  

The model that is the best is the one that uses the four variables: L1-L2-H-W.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```
```{r}
best.model <- lm(Weight~Length2+Width,data=Smeltdata)
fullup <- lm(Weight~.,data=Smeltdata)
summary(best.model)
```
```{r}
anova(fullup,best.model)
```

The p-value is to big to say that theirs a difference between the best model that uses four variables and the best model that uses two variables.

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Based on the automatic selection of variables there is no difference with using a model with two variables versus using one with all of the variables. This was identified through the adjusted R squared as well as the p-values. In conclusion comparing the p-values of the two variables models the p-value was so small that 
I reject the null hypothesis that these models are beneficial in predicting weight of fish. the prediction with the model is significantly better than our prediction that we may just by chance, or by using just a mean value.The p-values associated with the anova show that they fail to reject the null hypothesis because they are all large. Because there is no difference using the model with two variables versus the fullup models.




